---
title: "Linear Model with prediction"
author: "Wayne Jarvis"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 
require(tidyverse) 
require(knitr) 

data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE) 
```

### Model1: SIMS-ARM

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results

```{r}
cor(data$SIMS, data$ARM)
```

### Inferential Results

```{r}
model.1 <- lm(SIMS ~ ARM, data = data)
summary(model.1)
```

### Create Target

```{r}
target <- data.frame(ARM=90, GRIP=90)
```

### Predict Target Point of Model 1

```{r}
predict(model.1,target,interval=c("prediction"))
```

### Linear Fit Model1

```{r}
basicNN +
  geom_point() +
  ggtitle("SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5, size = 20)) +
  geom_smooth(method = "lm", se = FALSE, color = "red")
```

### Model 2

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```

```{r}
basicNN + geom_point() + ggtitle("SIMS vs ARM") + theme(plot.title = element_text(hjust = 0.5, size = 20))
```

### Numerical Results Model2

```{r}
cor(data$SIMS, data$ARM)
```

The correlation number for model2 (SIMS~ARM+GRIP) is higher compared to model2 (SIMS-GRIP) and model1 (SIMS-ARM), so the correlation is better when using both models (ARM and GRIP) rather than using one of them (either ARM or GRIP).

### Inferential Results Model2

```{r}
model.1 <- lm(SIMS ~ ARM, data = data)
summary(model.1)
```

The formula for getting model2 is: formula = -5.433871 + 0.037311*ARM + 0.24470*GRIP

### Predict Target Point of Model 2

```{r}
predict(model.1,target,interval=c("prediction"))
```



